### 2014-04-11 paper/discussion.tex
paper to send to gord

\emph{Aural} outputs can be created with gases.  Pipes and cavities can act as resonators can be leveraged to create 3D-printed sound chambers with explicitly designed sound characteristics~\cite{Zoran-flute} (see Figure \ref{fig:ocarina}).  %All that is necessary for this is an enclosed chamber with a pipe connected to it via a narrow neck-point (see Figure \ref{fig:ocarina}).  
Passive sound amplification and sound redirection are also possible using pipes, and sensing of some interactions, e.g., \emph{tapping and grasping}, can be sensed acoustically.  Due to differential sound conductivity in different printed materials, solid pipes of a material with greater conductivity (i.e., rigid, high-density) can be embedded in a model of a lesser conductivity (i.e., softer).  A microphone or piezo placed at the system-side of these sound-conducting pipes can determine where the model was tapped and how it was tapped.  Active acoustic sensing as described in Touch \& Activate \cite{Ono-touchandactivate} is also possible; this technique would allow for particular areas of interest (connected to rigid pipes) to be touch sensitive and enable grasp sensing.

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/placeholder/helmholz.jpg}
\caption{Some possible pipe uses.  The printed whistle in (a) is a Helmholz resonator: it creates a sound when air is blown through the pipe at the front, because air compresses at the small neck joint between the internal chamber and the pipe.  In (b), a capacitor manufactured on a 3D printer coated post-print with copper paint.  This particular one holds a charge of \valkyrie{XX}.  (c) gives a comparison of pipe-based resistors, also filled with copper paint.  For a cylindrical wire, resistance = $\rho\frac{l}{\pi r^2}$, where $\rho$ is based on the conductivity of the medium.  In our case, because $r << l$, $resistance(B) < resistance(C) < resistance(A)$.}
\label{fig:ocarina}
\end{figure}

@@

Printing or injecting conductive material can also be used to design passive components with particular electrical properties. For example, we printed a proof-of-concept  capacitor which features a thin printed plate with hollow cones on either side (see Figure \ref{fig:electronics}a).  After printing, we coated the inner surfaces of capacitor with copper paint.  It now can hold a charge of \valkyrie{xx}.  Similarly, tubes can be used to create \emph{resistors} in ``printed'' circuitry: a longer or thinner tube has a greater resistance than a shorter or wider one (see Figure \ref{fig:electronics}b).  Internal \emph{antenna} design is also possible, which could lead to new flexibility in, e.g., cell phone design (see Figure \ref{fig:electronics}c). Future design tools could help designers achieve desired electrical properties automatically.

>>>>

\emph{Aural} outputs can be created with gases.  Pipes and cavities can act as resonators can be leveraged to create 3D-printed sound chambers with explicitly designed sound characteristics~\cite{Zoran-flute} (see Figure \ref{fig:speculative}a).  %All that is necessary for this is an enclosed chamber with a pipe connected to it via a narrow neck-point (see Figure \ref{fig:ocarina}).  
Passive sound amplification and sound redirection are also possible using pipes, and sensing of some interactions, e.g., \emph{tapping and grasping}, can be sensed acoustically.  Due to differential sound conductivity in different printed materials, solid pipes of a material with greater conductivity (i.e., rigid, high-density) can be embedded in a model of a lesser conductivity (i.e., softer).  A microphone or piezo placed at the system-side of these sound-conducting pipes can determine where the model was tapped and how it was tapped.  Active acoustic sensing as described in Touch \& Activate \cite{Ono-touchandactivate} is also possible; this technique would allow for particular areas of interest (connected to rigid pipes) to be touch sensitive and enable grasp sensing.

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/speculative.png}
\caption{Some possible pipe uses.  The printed whistle in (a) is a Helmholz resonator: it creates a sound when air is blown through the pipe at the front, because air compresses at the small neck joint between the internal chamber and the pipe.  In (b), a capacitor manufactured on a 3D printer coated post-print with copper paint.  This particular one holds a charge of \valkyrie{XX}.  (c) gives a comparison of pipe-based resistors, also filled with copper paint.  For a cylindrical wire, resistance = $\rho\frac{l}{\pi r^2}$, where $\rho$ is based on the conductivity of the medium.  In our case, because $r << l$, $resistance(2) < resistance(3) < resistance(1)$.}
\label{fig:speculative}
\end{figure}

@@

Printing or injecting conductive material can also be used to design passive components with particular electrical properties. For example, we printed a proof-of-concept  capacitor which features a thin printed plate with hollow cones on either side (see Figure \ref{fig:speculative}b).  After printing, we coated the inner surfaces of capacitor with copper paint.  It now can hold a charge of \valkyrie{xx}.  Similarly, tubes can be used to create \emph{resistors} in ``printed'' circuitry: a longer or thinner tube has a greater resistance than a shorter or wider one (see Figure \ref{fig:speculative}c).  Internal \emph{antenna} design is also possible, which could lead to new flexibility in, e.g., cell phone design. Future design tools could help designers achieve desired electrical properties automatically.
